%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Activities \& Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Leader and Main Contributor} % Affiliation/role
    {CDRP Decomposition and Assembly (Course Project for Design and Analysis of Algorithms)} % Organization/group
    {Shanghai, China} % Location
    {Dec. 2019 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Proposed a network model fusion framework based on assembly of multiple small networks, and instantiated the framework based on Critical Data Routing Path decomposition.}
        \item {Top 5 among all teams and enters the workshop hosted by the advisor Jiang Li.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Leader and Main Contributor} % Affiliation/role
    {A Program Logic for Asymptotic Time Complexity (Course Project for Programming Language)} % Organization/group
    {Shanghai, China} % Location
    {May. 2019 - June. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Upgrade the regular program logic for While-Language to reason about asymptotic time complexity of the program.}
        \item {Proved the soundness of the logic and time complexity of some example programs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Main Contributor} % Affiliation/role
  {VEX Robotics Competition Selective Trial in SJTU} % Organization/group
  {Shanghai, China} % Location
  {July. 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Built a robot able to lift obstacle and shoot balls from scratch, and wrote the program using Robotc for manual control and automated control.}
      \item {Our team achieved top 5 among 20+ teams but did not enter the final.}
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}
