%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills \& Others}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}

%---------------------------------------------------------
  \cvskill
    {Programming} % Category
    {C/C++, Python, Coq, C\#, Matlab, LaTeX, Java, PHP} % Skills
%---------------------------------------------------------
\vspace{0.4em}
  \cvskill
    {Languages} % Category
    {Chinese, English, Japanese} % Skills

%---------------------------------------------------------
\vspace{0.8em}
  \cvskill
    {Formal Verification}
    {
      \hspace{-2.5em}
      \begin{minipage}{0.94\linewidth}
        \begin{itemize}
          \item As part of my research prerequisites, I learned to use Coq for formal verification and proof engineering.
          \item Have many experience with Coq projects, including \begin{itemize}
            \item the programming language course project about a program logic with asymptotic time complexity,
            \item verifying a bitwise algorithm,
            \item and the recent project about reentrancy in smart contracts.
          \end{itemize}
        \end{itemize}
      \end{minipage}
    }

%---------------------------------------------------------
\vspace{0.8em}
  \cvskill
    {Machine Learning} % Category
    {
      \hspace{-2.5em}
      \begin{minipage}{0.94\linewidth}
        \begin{itemize}
          \item Interested in machine learning during the freshman and sophomore year, and taught myself about basic machine learning and data mining techniques and some advanced topics including computer vision with deep learning and reinforce learning.
          \item Familiar with libraries in Python for machine learning development, including Numpy, Pandas, Scikit-Learn, TensorFlow, and Keras.
        \end{itemize}
      \end{minipage}
    } % Skills
  
%---------------------------------------------------------
\vspace{0.8em}
  \cvskill
  {Game Development}
  {
    \hspace{-2.5em}
    \begin{minipage}{0.94\linewidth}
      \begin{itemize}
        \item As a hobby, learned to create games using Unity game engine and C\# in the freshman year, and learned about Unreal engine for game programming in the sophomore year.
        \item Created a complete game using Unity engine and my own artworks in the sophomore year, and still interested in game development.
      \end{itemize}
    \end{minipage}
  }

%---------------------------------------------------------
\vspace{0.8em}
  \cvskill
  {Web Development}
  {
    \hspace{-2.5em}
    \begin{minipage}{0.94\linewidth}
      \begin{itemize}
        \item Gained some experience with web development in course projects of Introduction to Engineering for Electronic Information (B \& C), both projects win the first price in both courses.
        \item Familiar with front-end development based on Bootstrap framework, certain familiarity with back-end development using PHP and Python.
      \end{itemize}
    \end{minipage}
  }

%---------------------------------------------------------
\end{cvskills}
